Reasoning About a Machine with Local Capabilities

### 2018-05-14 toplas/paper.tex
Change the discussion of efficient memory range clearing to discuss the "Efficient Tagged Memory" paper's insights and refer to it.

Since local capabilities seem intended to provide a restricted form of revocation, perhaps capability machines like CHERI should consider to provide special support for this requirement.
Ideally, such support would take the form of a highly-optimized instruction for erasing a large block of memory.
However, from a discussion with the designers of the CHERI capability machine, we gather that it is not immediately clear whether and how such a primitive could be implemented efficiently in the CHERI context.
\itoplassug{Maybe refer to some of the papers
  reviewer A, esop mentions for stack clearing. See comment in tex file. }
% http://scale.eecs.berkeley.edu/papers/mmp-asplos2002.pdf
% https://www.usenix.org/legacy/event/osdi08/tech/full_papers/zeldovich/zeldovich_html/index.html
% http://users.ece.utexas.edu/~tiwari/pubs/MICRO-08-rangecache.pdf

>>>>

Since local capabilities seem intended to provide a restricted form of revocation, perhaps capability machines like CHERI should consider to provide special support for this requirement.
Ideally, such support would take the form of a highly-optimized instruction for erasing a large block of memory.
Recent work suggests that such a feature could perhaps be added to processors like CHERI, using a special hardware cache that tracks whether or not a memory location contains zero \citep{Joannou2017EfficientTaggedMemory}.
% http://scale.eecs.berkeley.edu/papers/mmp-asplos2002.pdf
% https://www.usenix.org/legacy/event/osdi08/tech/full_papers/zeldovich/zeldovich_html/index.html
% http://users.ece.utexas.edu/~tiwari/pubs/MICRO-08-rangecache.pdf
